---
title: "Discussao_ratones"
output: html_document
---

#Intro

This is a initial assessment of the results from the RATONES data base.

Anna measured 5 mice lines, 1 control strain (t), two lines for increased body weigth at 49 days (P49, s.increase and h.increase), and two lines for decreased body weigth (s.decrease and h.decrease). The mice in the h lines were also inbread for the first generations, while the s mice where not. The skull is described by 35 linear measurements, and we calculated covariance matrices of skull distances and log weigth.

#Objectives

Our main objective is to study how directional selection alters covariation patterns. While the mice where only selected for body weigth, we expect changes in cranial morphology via correlated selection due to genetic correlations between traits. 

Working hypothesis:

1. Cranial traits will respond to selection on weigth acording to the Lande equation.

1. Covariance structures will change due to directional selection in many ways:
    - Overall variation will descrease in selected lines;
    - Selected lines will be more integrated, as weigth is correlated with size;
    - Variation will be aligned with the response to selection;
1. Traits that are under selection in the same direction will become more integrated, traits selected in diferent directions will become less integrated.
1. Populations that respond in the direction of their variation

#Results

```{r, echo = FALSE, results='hide', warning=FALSE}
setwd("../")
source("/home//diogro/projects/ratones/R/bayseanStats.R")
```

Regarding overall matrix structure, we can see changes in the mean integration, where selected lines are more integrated, and also have lower flexibility and evolvability. This indicates more constraints. 

```{r, echo = FALSE}
size = 5
print(global_stats_plot + labs(y = "") + 
        theme(text = element_text(size=rel(size)), 
                                legend.text = element_text(size=rel(size)), 
                                legend.title = element_text(size=rel(size))))
```

Also, selected lines have lower total variation.

```{r}
trace = function(x) c(trace = sum(diag(x)))
ldply(r_models, function(x) adply(x$Ps, 1, trace)) %>%
  separate(.id, c( 'treatment', 'strain')) %>% 
  ggplot(aes(treatment, trace/35, group = interaction(treatment, strain), fill = strain)) + geom_boxplot() + theme_bw()
stats %>% separate(.id, c( 'treatment', 'strain')) %>% filter(variable == 'DZpc1') %>% filter(type == "treatment") %>% 
  ggplot(aes(treatment, value, group = interaction(treatment, strain, type), fill = strain)) + geom_boxplot() + theme_bw()
```

## Variation in specific directions

Control line always has more variation in all directions we look. Evolvability and flexibility are always larger in the control line, even after we control for the mean value of flexibility and evolvability.

##Modularity

No pattern of modularty apears in relation to traits that are increasing or decreasing.

#Conclusions

1. Variation in directly affected by directional selection, even in short time spans. All selected lines loose variation. 